Music Classification Using Convolutional Neural Networks

### 2019-12-15 docs/paper.tex
add fix
Create references to bibliography

    The final testing accuracy of the model is \textbf{0.61\%}. Below are the Classication Matrix and the final
    Classification Report.

@@

    \section*{References}

    References follow the acknowledgments. Use unnumbered first-level heading for
    the references. Any choice of citation style is acceptable as long as you are
    consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
    when listing the references. {\bf Remember that you can use more than eight
    pages as long as the additional pages contain \emph{only} cited references.}
    \medskip

    \small

    [1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
    connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
    (eds.), {\it Advances in Neural Information Processing Systems 7},
    pp.\ 609--616. Cambridge, MA: MIT Press.

    [2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
    Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
    TELOS/Springer--Verlag.

    [3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
    recall at excitatory recurrent synapses and cholinergic modulation in rat
    hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.

>>>>

    The final testing accuracy of the model is \textbf{61\%}. Below are the Classication Matrix and the final
    Classification Report.

@@

    \bibliographystyle{plain}
    \bibliography{bibs}
